### 2015-03-15 staticanalysis.tex
updates in summarisation

Watchdog summarisation is based on our lockset and watchdog race checking instrumentation and uses the Houdini~\cite{flanagan2001houdini} invariant inference algorithm (available in Boogie) to automatically compute summaries from a pool of automatically generated candidate invariants.

>>>>

Watchdog summarisation uses the Houdini~\cite{flanagan2001houdini} invariant inference algorithm (available inside Boogie) to automatically compute summaries (pre- and post-conditions and loop invariants) from a pool of \emph{candidate} invariants.

The candidate invariants are based on the global variables that \whoop instruments to perform lockset analysis and race checking (see Section~\ref{tech:method}). The key idea behind watchdog summarisation is that we automatically generate candidate invariants in the granularity of watched accesses. This means that for e.g. watched access \texttt{\$M.0[\$p0]} the entry point has performed a write access, but for \texttt{\$M.0[\$p1]} it has not. This reduces the false positives from reporting errors if only e.g. a field of a struct is racing, but the rest of the fields are not. An example of candidate post-conditions is the following:

\begin{boogie}
procedure foo$ep1(dev: int);
  ...
  ensures _b$ls$entrypoint1$0
    ==> WATCHED_ACCESS_$M.0 == dev + 4
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ls$entrypoint1$1
    ==> WATCHED_ACCESS_$M.0 == dev + 8
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$0
    ==> WATCHED_ACCESS_$M.0 == dev + 4
    ==> !WRITTEN_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$1
    ==> WATCHED_ACCESS_$M.0 == dev + 8
    ==> !WRITTEN_$M.0_$entrypoint1;
  ...
\end{boogie}
